Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-07-09 thirdPaper/draft/typeConeAssociahedra.tex
One typo
Auslander's result

In \cref{sec:clusterCategories}, we prove an analogue for cluster categories of M. Auslander's result~\cite{Auslander1984}. \arnau{Which result? Is it famous? Should we say something like Auslaunder's famous result from...? }
We are mainly motivated by the fact that it has for a consequence that the type cones of the cluster fans of finite type are simplicial.
However, this result is of independent interest and sheds new lights on the Grothendieck groups of cluster categories.

>>>>

In \cref{sec:clusterCategories}, we prove an analogue for cluster categories of a result of M. Auslander for module categories of Artin algebras~\cite{Auslander1984}. \arnau{Which result? Is it famous? Should we say something like Auslaunder's famous result from...? }\pg{I've reformulated slightly.  Auslander was extremely prolific :-)}
We are mainly motivated by the fact that it has for a consequence that the type cones of the cluster fans of finite type are simplicial.
However, this result is of independent interest and sheds new lights on the Grothendieck groups of cluster categories.
